Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
another comment
consistency
more comments; polishing
t2v

\subsection{Dynamic Slicing}

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  top-5  & top-10 \\
		\midrule

@@

\subsection{Results}

@@

\begin{table*}[h]
	\centering
	  \begin{tabular}{|l|ccc|cccc|c|}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{SFL+DS-$k$} & \multirow{2}{*}{\# Faults} \\

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\
		\midrule
		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
  \label{table:fsws}
\end{table*}

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\
		\midrule
		$<0$  & 20.00\% & 17.42\% \\
		$=0$  & 47.10\% & 37.42\% \\
		$>0$  & 32.90\% & 45.16\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
	\label{tab:diagnosis}
\end{table}
\normalsize

@@

\subsection{Threats to validity}

\section{Related Work}

@@

\subsection{\comb{}}

@@

\section*{Acknowledgments}

>>>>

\subsection{Dynamic Slicing}
\Rui{ehmm.. what is this section all about? }

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{k}  & \combpar{10} \\
		\midrule

@@

\subsection{Results}
\Rui{Results \& Discussion?}

@@

\begin{table*}[h]
	\centering
	  \begin{tabular}{|l|ccc|cccc|c|}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

		            & \% $k = 5$ & \% $k = 10$  & $\Delta$ & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Sof{@todo: Add absolute numbers for SFL}\Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
		\midrule
		$<0$  & 20.00\% & 17.42\% \\
		$=0$  & 47.10\% & 37.42\% \\
		$>0$  & 32.90\% & 45.16\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{}}}
	\label{tab:diagnosis}
\end{table}
\normalsize

@@

\subsection{Threats to validity}
%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community \Rui{cite d4j}.

A potential threat to construct validity relates to the choice of oracle generation
for the Lithium toolset. However, we argue that our choice is able to capture whether
a program is failing because of the same reason.

The main threat to internal validity lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}.
%
\section{Related Work}
\Rui{needs work...}

@@

\subsection{\comb{}}
\Rui{\comb{} ??}

@@

%\section*{Acknowledgments}
%include only after review.
